---
title: "build tree"
author: "MAT"
date: "1/17/2022"
output: html_document
---

# Based on https://github.com/huqiwen0313/speciesTree

## Packages

speciesTree is on github; see https://github.com/huqiwen0313/speciesTree for short tutorial - 3 species case

```{r}
library(conos)
library(pagoda2)
library(speciesTree)
library(Seurat)
```

## Load data

integrated is the integrated object

```{r}
setwd()
integrated <- readRDS()
```

expression.matrix is a sparse matrix variable genes x cells

meta_clusters is a named integer vector with cluster assignments for each cell

upperlevelinfo is a named character vector with class assignments for each cell

species_annot is a named character vector with species assignments for each cell

subsampledClusters is a list of 10 meta_clusters with 95% of the original cells

Extract data from integrated Seurat object

```{r}
# rename clusters
new.ids <- seq(1, length(levels(Idents(integrated))), by=1)
names(new.ids) <- levels(Idents(integrated))
integrated <- RenameIdents(integrated, new.ids)
```

```{r}
expression.matrix <- GetAssayData(integrated, slot="data", assay="integrated")
meta_clusters <- as.integer(Idents(integrated))
names(meta_clusters) <- names(Idents(integrated))
upperlevelinfo = NULL
species_annot <- integrated@meta.data$species
names(species_annot) <- rownames(integrated@meta.data)

```


## Run the code

```{r}
d <- cluster.matrix.expression.distances(t(expression.matrix), groups=meta_clusters, dist="cor",  useVariablegenes=FALSE,  use.scaled.data=TRUE)
dendr <- hclust(as.dist(d), method='ward.D2')
dend <- as.dendrogram(dendr)
# tree <- buildSpeciesTree(dend=dend, expMatrix=t(expression.matrix), subsampleClusters=NULL,  cls.groups=meta_clusters, upperlevelannot=NULL, species=species_annot, n.cores=10, renameCluster = FALSE)
```

the function buildSpeciesTree doesn't work, workaround below

```{r}
dendr <- TransferDend(dend, renameCluster = FALSE, cls.groups = meta_clusters)
cls.groups <- dendr$new.groups
dend <- dendr$dendrogram
leafcontent <- dendr$leafcontent
stability.measurements = NULL
dend <- AddTreeAttribute(dend, species_annot, leafcontent)
dend <- dendSetWidthBysize(dend, scale = 8)

colorpallete <- colorRampPalette(c("blue", "grey", "grey",  "grey", "red"))(101)
# dend <- dendSetColorByMixing(dend, species_annot, leafContent, colorpallete)
upperLevelnodes = NULL
```
 
dendSetColorByMixing doesn't work, debug below

```{r}
fac <- as.factor(species_annot)
totalCells <- table(fac)

# cc2col <- function(cc, rate=15, base=0.001){
#     cc <- round((cc[2:4]/totalCells)/sum(cc[2:4]/totalCells), 2)
#     cv <- cc
#     cv <- dexp(cv, rate)
#     cv <- cv/rate * (1-base)
#     col <- adjustcolor(rgb(cv[1],cv[2],cv[3], 1), offset = c(0.5, 0.5, 0.5, 0.1))
#     return(col)
# }

cc2col <- function(cc, rate=15, base=0.001){
  cc <- round((cc[2:3]/totalCells)/sum(cc[2:3]/totalCells), 2)
  cv <- round(cc[1]*100, 0)
        colorpallete <- colorRampPalette(c("blue", "grey", "grey", "grey", "red"))(101)
        col <- colorpallete[cv + 1]
}

cbm <- function(d,fac) {
    if(is.leaf(d)) {
      #lc <- fac[leafContent[[as.numeric(attr(d,'label'))]]]
      cc <- attr(d, "cc")
      col <- cc2col(cc)
      attr(d,"edgePar") <- c(attr(d,"edgePar"),list(col=col))
      return(d);
    } else {
      oa <- attributes(d);
      d <- lapply(d,cbm,fac=fac);
      attributes(d) <- oa;
      cc <- attr(d, "cc")
      col <- cc2col(cc)
      attr(d,"edgePar") <- c(attr(d,"edgePar"),list(col=col))
      return(d);
    }
  }
  
dend <- cbm(dend,species_annot)

tree <- dend
plot(tree)
```
