---
title: "scvi tutorial"
author: "alonso"
output: html_document
  df_print: paged
  toc: yes
  toc_float: no
date: |
      | Started on 06/01/2022
      | Compiled on 'r format (Sys.Date(), "%B %d, %Y")'
---

# Setup

Activate a local environment and install required R packages. We will use a previously created local environment created in Miniconda called scvi-env called from reticulate. 

```{r}
renv::init()

renv::install('reticulate')

library(reticulate)

renv::install('Seurat')
renv::install('ggplot2')
renv::install('png')
renv::install('BiocManager')
renv::install('devtools')
renv::install('cowplot')
renv::install("sctransform")

reticulate::use_condaenv("scvi-env", required = TRUE)
```

# Installing more packages

From BiocManager and sceasy. 

```{r}
BiocManager::install("SingleCellExperiment")
BiocManager::install("scater")
BiocManager::install("multtest")
BiocManager::install("glmGamPoi")

devtools::install_github('cellgeni/sceasy')
```

# Installing Python requirements

```{r}
reticulate::py_install('scanpy')
reticulate::py_install('python-igraph')
reticulate::py_install('louvain')
```

Saving r environment. 

```{r}
renv::snapshot()
```

# Loading packages

```{r warning=FALSE, message=FALSE}
library(ggplot2)
library(Seurat)
library(SeuratData)
library(SingleCellExperiment)
library(cowplot)
library(sceasy)
library(scater)
library(glmGamPoi)
```

# Integration test

We will use the merged object with raw counts generated in the **3sp_object_for_scvi.R** script, as well as the integration genes generated from the **3Species_integration_HPC.R** script.

```{r fig.height=10, fig.width=10}
scvi.int <- readRDS("scvi_tools_3sp_merged.rds")
comb.features <- readRDS("3sp_genes_3951_scvi.rds")

scvi.int <- scvi.int[comb.features]

adata <- convertFormat(scvi.int, from="seurat", to="anndata", main_layer="counts", drop_single_values=FALSE)
print(adata)

# run setup_anndata, use column species for batch
scvi$model$SCVI$setup_anndata(adata, batch_key = 'species')

# create the model
model = scvi$model$SCVI(adata)

# train the model
model$train()

# to specify the number of epochs when training:
# model$train(max_epochs = as.integer(400))

# get the latent representation
latent = model$get_latent_representation()

# put it back in our original Seurat object
latent <- as.matrix(latent)
rownames(latent) = colnames(scvi.int)
scvi.int[["scvi"]] <- CreateDimReducObject(embeddings = latent, key = "scvi_", assay = DefaultAssay(scvi.int))

library(cowplot)
# for jupyter notebook
options(repr.plot.width=10, repr.plot.height=8)

# Find clusters, then run UMAP, and visualize
scvi.int <- FindNeighbors(scvi.int, dims = 1:10, reduction = "scvi")
scvi.int <- FindClusters(scvi.int, resolution =1)

scvi.int <- RunUMAP(scvi.int, dims = 1:10, reduction = "scvi", n.components = 2)

saveRDS(scvi.int, file = "scvi-tools_3Sp_3951genes_v3.rds")

DimPlot(scvi.int, reduction = "umap", pt.size=1, label = T, label.size = 4, repel = TRUE, shuffle = TRUE, group.by = "species")# + NoLegend()
```

# 4 Species integration with scVI

```{r fig.height=10, fig.width=10}
scvi.int <- readRDS("scvi_tools_4sp_merged.rds")
comb.features <- readRDS("comb_features_4sp.rds")

scvi.int <- scvi.int[comb.features]

adata <- convertFormat(scvi.int, from="seurat", to="anndata", main_layer="counts", drop_single_values=FALSE)
print(adata)

# run setup_anndata, use column species for batch
scvi$model$SCVI$setup_anndata(adata, batch_key = 'species')

# create the model
model = scvi$model$SCVI(adata)

# train the model
model$train()

# to specify the number of epochs when training:
# model$train(max_epochs = as.integer(400))

# get the latent representation
latent = model$get_latent_representation()

# put it back in our original Seurat object
latent <- as.matrix(latent)
rownames(latent) = colnames(scvi.int)
scvi.int[["scvi"]] <- CreateDimReducObject(embeddings = latent, key = "scvi_", assay = DefaultAssay(scvi.int))

library(cowplot)
# for jupyter notebook
options(repr.plot.width=10, repr.plot.height=8)

# Find clusters, then run UMAP, and visualize
scvi.int <- FindNeighbors(scvi.int, dims = 1:10, reduction = "scvi")
scvi.int <- FindClusters(scvi.int, resolution =1)

scvi.int <- RunUMAP(scvi.int, dims = 1:10, reduction = "scvi", n.components = 2)

saveRDS(scvi.int, file = "4Sp_scvi_v1.rds")

DimPlot(scvi.int, reduction = "umap", pt.size=1, label = T, label.size = 4, repel = TRUE, shuffle = TRUE, group.by = "species")# + NoLegend()
```